Time Series Analysis of Chaotic Dynamical Systems with Recurrent Neural Networks

### 2019-04-24 doc/paper/paper.tex
add abstract

\begin{abstract}
This is a paper about chaos.
\end{abstract}

>>>>

\begin{abstract}

The predictive power of the recurrent neural networks known as the Echo
State Network is not as strong for chaotic problems. Measured by
Lyapunov Characteristic Exponents (LCE), a time series forecasting 
analysis was applied to highly chaotic systems: Lorenz System, Double
Pendulum, and Poincaré's solution to the restricted circular three body
problem. The Lorenz system had an LCE of 0.935 with a predictability
length of 1 Lyapunov time. The double pendulum had an LCE of 0.601, and
a predictability length of less than 1 Lyapunov time. The restricted
circular three body problem solution had an LCE of 0.176 and a
predictability power as strong as 10 Lyapunov times. 
Other methods may be applied to improve the results, but in general
it seems the predictability is very low for very chaotic systems.

\end{abstract}
